### 2017-05-15 Publications/Original Software Publications/Science of Computer Programming/reply letter/letter.tex
updating reply letter
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

\begin{quote}
\textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: does he mean C++? Shall we reference the paper from ECBS 2013 about ESBMC++? Yes, please. Mention that we support C++ and cite our ECBS 2013 paper.}}
\end{quote}

>>>>

\begin{quote}
\textcolor{blue}{\textbf{Response:} Since 2013, ESBMC supports C++. We have added a reference to the paper ``SMT-Based Bounded Model Checking of C++ Programs'', which describes such work.}
\end{quote}
